### 2020-06-14 report/sections/general/theory/syntax.tex
Report: complete chapter 8.2
Report: complete up to deadlock freedom

\begin{figure}[!h]
\doublespacing
\[
\begin{array}{rlr}
G ::= & \dots & \text{Global Types} \\
\mid & \groute{p}{q}{s}{l_i: G_i}{i \in I}
& \text{Routed Communication through $\role{s}$} \\
\end{array}
\]
\singlespacing
\captionof{figure}{Global Types in \newtheory}
\label{fig:newsyntaxglobal}
\end{figure}

The new construct $\groute{p}{q}{s}{l_i: G_i}{i \in I}$ reads, 
\textit{
``the communication $\gcomm{p}{q}{l_i: G_i}{i \in I}$
is routed by $\role{s}$''
}.
To be more verbose,
$\role{p}$ offers $\role{q}$ a set of choices
$\left\{l_i\right\}_{i \in I}$,
$\role{q}$ sends their choice to
$\role{s}$, so $\role{p}$ receives the
selection $l_i$ made by $\role{q}$ via $\role{s}$,
and the communication system proceeds with continuation $G_i$.
We refer to $\role{s}$ hereafter as the \textit{router}.
$\role{s}$ ranges over the set of roles 
$\role{p},\role{q},\role{r},\role{s},\dots$,
but we use $\role{s}$ by convention as the server endpoint
is usually the router.

@@

\pt{\dots} & = & \dots \\

@@

\begin{figure}[!h]
\doublespacing
\[
\begin{array}{rlr}
T ::= & \dots & \text{Local Types} \\
\mid & \router{p}{q}{l_i: T_i}{i \in I}
& \text{Routing communication from $\role{p}$ to $\role{q}$} \\
\mid & \tselproxy{p}{q}{l_i: T_i}{i \in I}
& \text{Selecting from $\role{p}$ via proxy $\role{q}$} \\
\mid & \tbraproxy{p}{q}{l_i: T_i}{i \in I}
& \text{Receiving from $\role{p}$ via proxy $\role{q}$} \\
\end{array}
\]
\singlespacing
\captionof{figure}{Global Types in \newtheory}
\label{fig:newsyntaxlocal}
\end{figure}

@@

As shown in the last (4th) case, 
the same concept of \textit{merging}
applies for routed communication:
when projecting a routed communication
onto a non-participant, the projections of
all continuations must be ``compatible'',
namely they can be merged using the
the \textit{merging operator}, $\mergeop$.

As the merging operator is defined on local
types, we extend the merging operator to be defined
on the extended syntax in \cref{def:newmerge}.
Recall that proxy selection and proxy
branching behave in the same way as their ``non-proxified''
counterparts -- the merging operator reflects this
similarity.

\begin{definition}[Merging Operator]
The merging operator $\mergeop$ on local types
is defined as:

@@

@@

% characteristics of router as centroid
\begin{definition}[Centroid]
Let $\centroid{G}{s}$ denote \dots

>>>>

\begin{figure}[!h]
\doublespacing
\[
\begin{array}{rlr}
G ::= & & \text{Global Types} \\
\mid & \tend & \text{Termination} \\
\mid & \trecvar & \text{Type Variable} \\
\mid & \trec{G} & \text{Recursive Type} \\
\mid & \gcomm{p}{q}{l_i: G_i}{i \in I} & \text{Direct Communication} \\
\mid & \groute{p}{q}{s}{l_i: G_i}{i \in I}
	& \text{\hl{Routed Communication}} \\
\end{array}
\]
\singlespacing
\captionof{figure}{Global Types in \newtheory}
\label{fig:newsyntaxglobal}
\end{figure}

The new construct $\groute{p}{q}{s}{l_i: G_i}{i \in I}$ reads, 
\textit{
``the communication $\gcomm{p}{q}{l_i: G_i}{i \in I}$
is routed by $\role{s}$''
}.
To be more verbose,
$\role{p}$ offers $\role{q}$ a set of choices
$\left\{l_i\right\}_{i \in I}$,
$\role{q}$ sends their choice to
$\role{s}$, so $\role{p}$ receives the
selection $l_i$ made by $\role{q}$ via $\role{s}$,
and the communication system proceeds with continuation $G_i$.
We refer to $\role{s}$ hereafter as the \textit{router}.
$\role{s}$ ranges over the set of roles 
$\role{p},\role{q},\role{r},\role{s},\dots$,
but we use $\role{s}$ by convention as the server endpoint
is usually the router.
Just as it is assumed that $\role{p} \neq \role{q}$ for
direct communication,
we also assume that
$\role{p} \neq \role{q} \neq \role{s}$ for routed communication.

@@

@@

\begin{figure}[!h]
\doublespacing
\[
\begin{array}{rlr}
T ::= &  & \text{Local Types} \\
\mid & \tend & \text{Termination} \\
\mid & \trecvar & \text{Type Variable} \\
\mid & \trec{T} & \text{Recursive Type} \\
\mid & \tsel{p}{l_i: T_i}{i \in I} & \text{Selection} \\
\mid & \tbra{p}{l_i: T_i}{i \in I} & \text{Branching} \\
\mid & \router{p}{q}{l_i: T_i}{i \in I}
& \text{\hl{Routing Communication}} \\
\mid & \tselproxy{p}{q}{l_i: T_i}{i \in I}
& \text{\hl{Proxy Selection}} \\
\mid & \tbraproxy{p}{q}{l_i: T_i}{i \in I}
& \text{\hl{Proxy Branching}} \\
\end{array}
\]
\singlespacing
\captionof{figure}{Global Types in \newtheory}
\label{fig:newsyntaxlocal}
\end{figure}

@@

As shown in the last (4th) case, 
the same concept of \textit{merging}
applies for routed communication:
when projecting a routed communication
onto a non-participant, the projections of
all continuations must be ``compatible'',
namely they can be merged using the
the \textit{merging operator}, $\mergeop$.
As the merging operator is defined on local
types, we extend the merging operator to be defined
on the extended syntax in \cref{def:newmerge}.

\begin{definition}[Merging Operator]
The merging operator $\mergeop$ on local types
is:

@@

Recall that proxy selection and proxy
branching behave in the same way as their ``non-proxified''
counterparts -- the merging operator reflects this
similarity.

@@

% characteristics of router as centroid
\begin{definition}[Centroid]
Let $\centroid{G}{s}$ denote that $\mrole{s}$ is the 
centroid of $G$.
